Deciding to Disclose

### 2015-09-15 Results.tex
Make it more obvious
That heavy & moderate pool because it is low risk for both

Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.

>>>>

Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so. This arises because both classes of agent learn that the moderate signal is the lower risk option as it is both a reliable indicator of need, and does not attract strongly negative judgement. The reliability of the signal is self reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.
